### 2014-02-28 thesis/src/appendices/glossary.tex
Thesis: add the part of a glossary

>>>>

\newglossaryentry{adaptable system}{name={adaptable system},  description={
An adaptable system is a system that has the following attributes:
\begin{inparaenum}[1)]
\item it can monitor its state and take appropriate actions,
\item IT staff is responsible for managing performance against SLAs and
\item the human interaction should be at the minimal level.
\end{inparaenum}
}}

\newglossaryentry{autonomic system}{name={autonomic system},  description={ A
system with the ability to manage itself and dynamically adapt to change in
accordance with business policies and objectives. Self-managing environments
can perform such activities based on situations they observe or sense in the IT
environment rather than requiring IT professionals to initiate the task.  These
environments are self-configuring, self-healing, self-optimizing, and
self-protecting.  }}

\newglossaryentry{lightweight virtualization}{name={lightweight
virtualization}, description={ Lightweight or operating system–level
  virtualization is a server virtualization method where the kernel of an
  operating system allows for multiple isolated user-space instances, instead
  of just one. Such instances (often called containers, virtualization engines
(VE), virtual private servers (VPS) or jails) may look and feel like a real
server, from the point of view of its owner. }}

\newglossaryentry{horizontal scalability}{name={horizontal scaling},
description={ The ability to connect multiple hardware or software entities,
such as virtual machines, so that they work as a single logical unit.  }}

\newglossaryentry{vertical scalability}{name={vertical scaling}, description={
The ability to increase the capacity of existing hardware or software by adding
resources - for example, adding processing power to a server to make it faster
}}

\newglossaryentry{hybrid cloud}{name={hybrid cloud},  description={
The cloud infrastructure is a composition of two or more distinct cloud
infrastructures (private, community, or public) that remain unique entities,
but are bound together by standardized or proprietary technology that enables
data and application portability (e.g., cloud bursting for load balancing
between clouds)
}}

\newglossaryentry{cloud bursting}{name={cloud bursting},  description={
A deployment model which enables seamless resource infrastructure scaling for
a cloud customer which has its own private cloud. It relies on the concept of
using resources provided by an external provider for a given time interval 
when necessary, e.g. in case of a sudden spike in demand of a web application
}}
